My wonderful paper

### 2024-10-17 _manuscript/_tex/index.tex
add some prompts to the paper

@@

@@

>>>>

In a data analysis workflow -\textgreater{} going back to diagnose the
descripency between the expectation and the result is often
time-consuming and challenging.

For consumers of data analysis, it is often difficult to evaluate the
analysis outcome. Not always have the script to run, even difficult when
different expectations are held.

We propose here a concept called analysis plan to make the expectation
of the analysis process explicit. It can help to guide the analysis
process, to communicate and compare the analysis process to others, and
to evaluate the analysis process. (think more closer here how our
approach help to solve the problem)

@@

\section{Method}\label{method}

\subsection{Toy example revisited}\label{toy-example-revisited}

\begin{itemize}
\item
  provide interpretation at different scenarios:

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi})}
  \tightlist
  \item
    one test is flagged, the prediction is as expected:
  \item
    multiple tests are flagged, the prediction is unexpected,
  \item
    no test is flagged, the prediction is unexpected,
  \item
    no test is flagged, the prediction is as expected
  \end{enumerate}
\end{itemize}

@@

\section{Discussion}\label{discussion}

\begin{itemize}
\item
  how to systematically simulate data is still unknown, sensitivity of
  the simulation to the resutls
\item
  currently no automated way to generate unit tests
\end{itemize}

### 2024-10-17 index.qmd
add some prompts to the paper

@@

@@

>>>>

In a data analysis workflow -> going back to diagnose the descripency between the expectation and the result is often time-consuming and challenging.

For consumers of data analysis, it is often difficult to evaluate the analysis outcome. Not always have the script to run, even difficult when different expectations are held.

We propose here a concept called analysis plan to make the expectation of the analysis process explicit. It can help to guide the analysis process, to communicate and compare the analysis process to others, and to evaluate the analysis process. (think more closer here how our approach help to solve the problem)

@@

# Method

## Toy example revisited

* provide interpretation at different scenarios:

  1) one test is flagged, the prediction is as expected: 
  2) multiple tests are flagged, the prediction is unexpected, 
  3) no test is flagged, the prediction is unexpected, 
  4) no test is flagged, the prediction is as expected

@@

# Discussion

* how to systematically simulate data is still unknown, sensitivity of the simulation to the resutls

* currently no automated way to generate unit tests
